Cover Letter

### 2017-12-26 paper/cover_letter.tex
paper: wordsmithing
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%Experimental Setup (R1, R2, R3)
%- code R1
%- servers, network, storage R1, R3
\section*{Issue I: No Experimental Setup (Reviewers 1, 2, and 3)}

We apologize for the omission of experimental setup and source code details. To
provide a more comprehensive view of our experiments, we added text to the
paper and made paper artifacts available online. For the experimental setup, we
describe the cluster setup (hardware, software, etc.) in Section~{\S}V.  We
have also made the infrastructure code available and added links after each
figure to show exactly how experiments are run.  This infrastructure code
contains scripts to deploy the system, run experiments, and gather results.
This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  For the source code, we have added code
snippets to the evaluation to concretize what was actually done and made the
source code available online. A link is provided in a footnote in
Section~{\S}V.

@@

All reviewers note that the results and contributions we cite in the
introduction are not validated, explained, or even mentioned in the evaluation.
One confusing component of this issue is that we mixed future work with the
contributions of this paper; to make the contributions more explicit we remove
future work from the introduction and add it to the future work section in
Section~{\S}VI. We also connect all numbers we cite in the introduction to the
evaluation. To further clarify the evaluation, we:

@@

  \item added raw numbers (as annotations) to the baselines in each figure.
This helps the reader calculate the raw numbers instead of just relying on
overhead and speedup numbers.

  \item re-organized the section to make experiments more independent and
removed cross-references. Experiments are now self-contained so the reader can
see the effects of different API configurations and we do a better job of
explaining how results are derived.

  \item removed the ``major takeaways". We deleted the headings but left the
conclusions we make as transitions. We also add insights into the results by
analyzing the raw numbers we observe in comparison to hardware capabilities.

@@

%Use Cases R2, R4
%- Spark discussion R2
%- more emphasis on parallel and distributed computing themes R4
\section*{Issue III: Synthetic and/or Irrelevant Use Cases (Reviewers 2 and 4)}

We add a section to the introduction that scopes the importance of storage for
large scale runtimes and workflows. Parallel and distributed jobs (whether they
are MPI-based, MapReduce-based, etc.) need parallel and distributed storage
systems that keep up with the computation. Furthermore, we highlight the
parallel and distributed computing themes and cast light on them from the
context of our prototype. We also add the Spark discussion proposed by to the
evaluation. The goal is to show how a system such as Cudele would benefit from
more general runtimes. We also move the discussion about the potential for HDFS
and CephFS subtrees in the same namespace and the cost of dynamically changing
consistency and durability semantics on a subtree.

>>>>

%Use Cases R2, R4
%- Spark discussion R2
%- more emphasis on parallel and distributed computing themes R4
\section*{Issue I: Synthetic and/or Irrelevant Use Cases (Reviewers 2 and 4)}

To show the relevance of the use cases, we re-wrote Section~{\S}V-B to
highlight examples from HPC and cloud workloads that would benefit from using
Cudele. For HPC we focus on user home directories used for experiments and for
the cloud we focus on the Hadoop and Spark runtimes (as suggested by Reviewer
2). To connect the problematic use cases to Cudele, we added \textbf{Cudele
setup} headers in Section~{\S}V-B to show which subtree semantics accomodate
these workloads in the global namespace.  By showing these setups, we hope to
demonstrate that different applications can use a file system in parallel with
different consistency/durability semantics.  Although we do not actually run
the workloads on our prototype, hopefully our changes show how the use cases,
and the synthetic benchmarks we used to represent them, are indeed relevant to
parallel and distributed computing.

To align the paper to the themes of the conference, we changed Section~{\S}V-A
and Figures 6a, 6b, and 6c to emphasize that decoupled namespaces facilitate
client-driven parallelism. Clients detach subtrees form the global namespaces
and do operations in-parallel to their local disk. We also hope that changes to
the use cases above motivates the need for robust distributed storage systems
that can handle today's applications.  So while the paper is storage-centric,
we try to show that the workloads it supports are highly distributed and need a
flexible solution like Cudele.

@@

All reviewers note that the results and contributions we cite in the
introduction are not validated, explained, or even mentioned in the evaluation.
One confusing component of this issue is that we mixed future work with the
contributions of the paper; to make the contributions more explicit we remove
future work from the introduction and add it to Section~{\S}VI; we do not
attempt to validate or prove any of the statements about the benefits of
changing consistency and durability properties of a subtree dynamically, such
as saving resource provisioning costs.  To further clarify the evaluation, we:

@@

  \item explicitly state the Cudele setups and subtree configurations in bold
in Section~{\S}V-A. Hopefully this helps the reader keep track of use cases and
demonstrates how Cudele might be able to help in these scenarios.

and include baseline values in the
text so readers can quickly calculate raw numbers from our speedup/slowdown
graphs. We also make sure to connect all speedups from the introduction to the
evaluation. We hope this clarifies confusion about what we are comparing to
when we reference speedups and slowdowns.

  \item re-organized the sections and removed cross-references. Experiments are
now self-contained so the reader can see the effects of different API
configurations and we do a better job of explaining how results are derived.

  \item removed the ``major takeaways". We deleted the headings but moved the
text to the beginning of each section to motivate why we are doing each
experiment.  We also add insights into the results by analyzing the raw numbers
we observe in comparison to hardware capabilities.

  \item re-labeled all graphs with the same metric (throughput
slowdown/speedup) and aligned Section~{\S}V with the graphs in Section~{\S}II.
We hope this eliminates more of the confusion triggered by the
cross-referencing we did, referenced by Reviewers 2 and 3.

@@

%Experimental Setup (R1, R2, R3)
%- code R1
%- servers, network, storage R1, R3
\section*{Issue III: No Experimental Setup (Reviewers 1, 2, and 3)}

We apologize for the omission of experimental setup and source code details. To
provide a more comprehensive view of our experiments, we added text to the
paper and made paper artifacts available online. For the experimental setup, we
describe the cluster setup (hardware, software, etc.) in Section~{\S}V.  We
have also made the infrastructure code available and added links after each
figure to show exactly how experiments are run.  This infrastructure code
contains scripts to deploy the system, run experiments, and gather results.
This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  We also made the source code available
online and a link is provided in a footnote in Section~{\S}V. Finally, we add
details about which tools and classes we modified in Section~{\S}IV to address
Reviewer 1's questions about the framework implementation.

### 2017-12-26 paper/sections/0_abstract.tex
paper: wordsmithing
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show 8\(\times\) speedup and 2\(\times\) scale when compared to our baseline
system.

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show similar speedups to related work \newcomment{but more importantly, our
prototype can custom fit subtrees in the same namespace to applications common
in large data centers, such as checkpoint-restart (91.7\(\times\), user home
directories (within a 0.03 standard deviation from optimal), and clients
checking for partial results (only a 2\% overhead).}  \oldcomment{ and can
scale to 2\(\times\) as many clients when compared to our baseline system.}

### 2017-12-26 paper/sections/5_implementation.tex
paper: wordsmithing
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% how it works in CephFS
\textbf{Metadata Store}: In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse.

@@

\textbf{Journal}: The journal is the second way that CephFS represents the file system namespace;
it is a log of metadata updates that can materialize the namespace when the
updates are replayed onto the metadata store. The journal is a ``pile system";
writes are fast but reads are slow because state must be reconstructed.
Specifically, reads are slow because there is more state to read, it is
unorganized, and many of the updates may be redundant.

@@

\textbf{Journal Tool}: The journal tool is used for disaster recovery and lets administrators view and
modify the journal. It can read the journal, export the journal as a file,
erase events, and apply updates to the metadata store.  To apply journal
updates to the metadata store, the journal tool reads the journal from object
store objects and replays the updates on the metadata store in the object
store.

@@

\textbf{Inode Cache}: In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For example, if a client or
metadata server is not caching the directory inode, all creates within that
directory will result in a lookup and a create request. If the directory inode
is cached then only the create needs to be sent.  The size of the inode cache
is configurable so as not to saturate the memory on the metadata server --
inodes in CephFS are about 1400
bytes\footnote{http://docs.ceph.com/docs/jewel/dev/mds\_internals/data-structures/}.
The inode cache has code for manipulating inode numbers, such as pre-allocating
inodes to clients.

@@

\textbf{Large Inodes}: In CephFS, inodes already store policies, like how the file is striped
across the object store or for managing subtrees for load balancing. These
policies adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other.

>>>>

% how it works in CephFS
\subsection{Metadata Store}

In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse.

@@

\subsection{Journal}

The journal is the second way that CephFS represents the
file system namespace; it is a log of metadata updates that can materialize the
namespace when the updates are replayed onto the metadata store. The journal is
a ``pile system"; writes are fast but reads are slow because state must be
reconstructed.  Specifically, reads are slow because there is more state to
read, it is unorganized, and many of the updates may be redundant.

@@

\subsection{Journal Tool}

The journal tool is used for disaster recovery and lets administrators view and
modify the journal. It can read the journal, export the journal as a file,
erase events, and apply updates to the metadata store.  To apply journal
updates to the metadata store, the journal tool reads the journal from object
store objects and replays the updates on the metadata store in the object
store.

@@

\subsection{Inode Cache}

In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For
example, if a client or metadata server is not caching the directory inode, all
creates within that directory will result in a lookup and a create request. If
the directory inode is cached then only the create needs to be sent.  The size
of the inode cache is configurable so as not to saturate the memory on the
metadata server -- inodes in CephFS are about 1400
bytes\footnote{http://docs.ceph.com/docs/jewel/dev/mds\_internals/data-structures/}.
The inode cache has code for manipulating inode numbers, such as pre-allocating
inodes to clients.

@@

\subsection{Large Inodes}

In CephFS, inodes already store policies, like how the file is striped
across the object store or for managing subtrees for load balancing. These
policies adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other.
